### 2023-11-14 README.Rmd
update readme
readme
fix pathing

Prerequisites:
 - docker
 - nvidia-container-toolkit

@@

```{bash eval=FALSE}
# -e DISABLE_AUTH=true --shm-size 50G
sudo docker run \
  -v "$(pwd):/workspace/rofcamtrap" \
  -v "/media/vlucet/TrailCamST/TrailCamStorage:/workspace/storage/TrailCamStorage" \
  -v "/media/vlucet/My Passport/Images:/workspace/storage/my_passport_images" \
  --gpus all \
  -it rofcamtrap
```

@@

```{bash eval=FALSE}
mamba activate cameratraps-detector
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \ 
  -m "/workspace/models/md_v5a.0.0.pt" \
  md
```

@@

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/0_outputs" \
  repeat-detect
```

@@

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/0_outputs" \
  -o "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats" \
  repeat-remove
```

@@

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/" \
  -o "/workspace/rofcamtrap/1_MegaDetector/2_visualize/" \
  viz
```

@@

```{bash eval=FALSE}
mamba deactivate 
cd mdtools
poetry shell
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/" \
  -o "/workspace/rofcamtrap/2_LabelStudio/0_inputs/" \
  repeat-convert
```

@@

On beluga, we use the apptainer iamge instead.

@@

>>>>

Prerequisites:

  - docker
  - nvidia-container-toolkit

@@

```{bash eval=FALSE}
# -e DISABLE_AUTH=true --shm-size 50G
docker run \
  -v "$(pwd):/workspace/rofcamtrap" \
  -v "/media/vlucet/TrailCamST/TrailCamStorage:/workspace/storage/TrailCamStorage" \
  -v "/media/vlucet/TrailCamST/TrailCamStorage_2:/workspace/storage/TrailCamStorage_2" \
  --gpus all \
  -it rofcamtrap
```

@@

```{bash eval=FALSE}
mamba activate cameratraps-detector
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -m "/workspace/models/md_v5a.0.0.pt" \
  -o "/workspace/rofcamtrap/1_MegaDetector/0_outputs/TrailCamStorage_2" \
  md
```

@@

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/1_MegaDetector/0_outputs/TrailCamStorage_2" \
  repeat-detect
```

@@

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/1_MegaDetector/0_outputs/TrailCamStorage_2" \
  -o "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/TrailCamStorage_2" \
  repeat-remove
```

@@

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/TrailCamStorage_2" \
  -o "/workspace/rofcamtrap/1_MegaDetector/2_visualize/TrailCamStorage_2" \
  viz
```

@@

```{bash eval=FALSE}
mamba deactivate 
cd mdtools
poetry shell
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/TrailCamStorage_2" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/TrailCamStorage_2" \
  -o "/workspace/rofcamtrap/2_LabelStudio/0_inputs/TrailCamStorage_2" \
  repeat-convert
```

@@

On beluga, we use the apptainer image instead.

@@

We need to download the models... TBA
